---
title: "PBSR ASSIGNMENT 2"
author: "SHREYAN CHAKRABORTY"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(tidyverse)
library(quantmod)
getSymbols('TCS.NS')
tail(TCS.NS)

```

```{r}
plot(TCS.NS$TCS.NS.Adjusted)
```
```{r}
getSymbols('^NSEI')
tail(NSEI)
```
```{r}
plot(NSEI$NSEI.Adjusted)
```
```{r}
TCS_rt = diff(log(TCS.NS$TCS.NS.Adjusted))
Nifty_rt = diff(log(NSEI$NSEI.Adjusted))
retrn = cbind.xts(TCS_rt,Nifty_rt)
retrn = na.omit(data.frame(retrn))
plot(retrn$NSEI.Adjusted,retrn$TCS.NS.Adjusted
     ,pch=20
     ,xlab='Market Return'
     ,ylab='TCS Return'
     ,xlim=c(-0.18,0.18)
     ,ylim=c(-0.18,0.18))
grid(col='grey',lty=1)

```

where $\mathbb{E}(\varepsilon)=0$ and $\mathbb{V}ar(\varepsilon)=\sigma^2$.

1. Estimate the parameters of the models $\theta=(\alpha,\beta,\sigma)$ using the method of moments type plug-in estimator discussed in the class.

2. Estimate the parameters using the `lm` built-in function of `R`. Note that `lm` using the OLS method.



```{r}
#For method of moment estimation, the equations are as follows:
#E(TCS)=alpha +beta*E(Nifty)
#E(Nifty(TCS-alpha-beta*Nifty))=0
#E(TCS-alpha-beta*Nifty)^2=sigma^2
attach(retrn)
tail(retrn)

#creating a 2X2 coefficient matrix for solving of system of equations:
x<-array(0,4)
x[1] = 1
x[2] <- mean(NSEI.Adjusted)
x[3] <- mean(NSEI.Adjusted)
x[4] <- mean((NSEI.Adjusted)*(NSEI.Adjusted))
A <- matrix(x,nrow=2)

#inserting another column containing TCS*NSE value named as "C"
retrn <- retrn %>% 
    mutate(C=TCS.NS.Adjusted*NSEI.Adjusted)

#storing values in 2X1 matrix for solving of system of equations:
y <- array(0,2)
y[1] <- mean(TCS.NS.Adjusted)
y[2] <- mean(C)
B <- matrix(y,ncol=1)
par_solution <- solve(A,B)

#Now estimating through OLS using lm function
model_ols <- lm(TCS.NS.Adjusted~NSEI.Adjusted,retrn)
summary(model_ols)
matrix_coeff <- summary(model_ols)$coefficients
plot(model_ols)
x<-var(model_ols$residuals)**0.5

#estimating sigma^2
sigma_2 <- mean((TCS.NS.Adjusted-par_solution[1,1]-par_solution[2,1]*NSEI.Adjusted)*(TCS.NS.Adjusted-par_solution[1,1]-par_solution[2,1]*NSEI.Adjusted))

#unbiased estimator of sigma_2
usigma_2 <- sigma_2*(length(TCS.NS.Adjusted)/(length(TCS.NS.Adjusted)-1))
usigma<-usigma_2**0.5

Parameter_List<-data.frame(Parameters=c('alpha','beta','sigma'),
                           MoM=c(par_solution[1,1],par_solution[2,1],usigma_2**0.5),
                           OLS=c(model_ols$coefficients[1],model_ols$coefficients[2],var(model_ols$residuals)**0.5))

```
```{r}
Parameter_List
```

3. Fill-up the following table

Parameters | Method of Moments         | OLS
-----------|---------------------------|-------------------------------
$\alpha$   |   `r par_solution[1,1]`   |`r model_ols$coefficients[1]`
$\beta$    |   `r par_solution[2,1]`   |`r model_ols$coefficients[2]`
$\sigma$   |   `r usigma`              |`r x`

```{r}
n_ft <-c(log(18200)-log(18000))
n_tcs<-predict(model_ols,newdata = data.frame(NSEI.Adjusted=n_ft))
New_value<-exp(n_tcs+log(3200))

```


4. If the current value of Nifty is 18000 and it goes up to 18200. The current value of TCS is Rs. 3200/-. How much you can expect TCS price to go up?


Ans:) The predicted price of TCS is `r New_value`



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
